---
title: "Typologies Maps and Figures"
author: "Laura Nelson"
date: "2024-12-12"
output: 
  html_document:
   toc: true
   toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#### Instructions

Each cluster result and the final typologies are shown below in interactive maps. You can zoom in, pan around, and click on a place to see the community and associated cluster/typology result. Bar plots are also included which show the count of communities in each cluster and typology.
```{r message=FALSE, warning=FALSE, include=FALSE}
require(sf)
require(mapview)
require(tidyverse)
library(RColorBrewer)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
econ <- st_read("./econ_spatial_places.shp") %>% select(NAME, state, cluster, geometry)
social_vul <- st_read("./sv_spatial_places.shp") %>% select(NAME, State, cluster, geometry)
energy <- st_read("./en_spatial_places.shp") %>% select(NAME, State, cluster, geometry)
typology <- st_read("./typology_2.shp") %>% select(NAME, State, ctypo, ecn_cls, en_clst, sv_clst, geometry)
port_typology <- st_read("./port_5000m_typologies.shp")  %>% select(NAME, State, ctypo, ecn_cls, en_clst, sv_clst, geometry)
ports <- st_read("./osw_suitable_ports.shp") %>% select(Name, geometry)

#st_layers(dsn = "./BOEM_Renewable_Energy_Geodatabase_0/BOEM_Renewable_Energy_Geodatabase.gdb/")
lease_areas <- st_read("./BOEM_Renewable_Energy_Geodatabase_0/BOEM_Renewable_Energy_Geodatabase.gdb/", layer = "BOEM_Wind_Lease_Outlines_06_06_2024") %>% filter(STATE == "CA")  
planning_areas <- st_read("./BOEM_Renewable_Energy_Geodatabase_0/BOEM_Renewable_Energy_Geodatabase.gdb/", layer = "BOEM_Wind_Planning_Area_Outlines_04_29_2024") %>% filter(CATEGORY1 == "Oregon Proposed Sale Notice (PSN)")
```

## Results
```{r message=FALSE, warning=FALSE, include=FALSE}
#display.brewer.pal(n = 3, name = 'RdYlBu')

pallete <- c("#6e7cb9","#7bbcd5", "#f5db99","#e89c81","#a45851")
#pallete <-rev(brewer.pal(5, "RdYlBu"))
pallete2 <- pallete[1:3]

require(paletteer)
cp <-paletteer_c("ggthemes::Sunset-Sunrise Diverging", 31)
cp
# 
# set.seed(7)
# cp2 <- sample(cp)
# cp2

cp2 <- cp[c(1:6,9,23,29,30,31)]
cp2
```
### Economic Cluster

```{r echo=FALSE, message=FALSE, warning=FALSE}
mapview(econ, zcol = "cluster", col.regions=pallete) + mapview(lease_areas, col.regions = "magenta") + mapview(planning_areas, col.regions = "lightpink")
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
require(ggplot2)
ggplot(econ, aes(x=cluster, fill = cluster)) + 
  geom_bar()+
    scale_fill_manual(values=c("#6e7cb9","#7bbcd5", "#f5db99","#e89c81","#a45851"))+
  geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.25)+
  theme_bw()+
  theme(legend.position="none",panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

### Social Vulnerability Cluster

```{r echo=FALSE, message=FALSE, warning=FALSE}
mapview(social_vul, zcol = "cluster", col.regions=pallete2) + mapview(lease_areas, col.regions = "magenta") + mapview(planning_areas, col.regions = "lightpink")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(social_vul, aes(x=cluster, fill = cluster)) + 
  geom_bar()+
    scale_fill_manual(values=c("#6e7cb9","#7bbcd5", "#f5db99"))+
  geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.25)+
  theme_bw()+
  theme(legend.position="none",panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
```

### Energy Cluster

```{r echo=FALSE, message=FALSE, warning=FALSE}
mapview(energy, zcol = "cluster", col.regions= pallete2) + mapview(lease_areas, col.regions = "magenta") + mapview(planning_areas, col.regions = "lightpink")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(energy, aes(x=cluster, fill = cluster)) + 
  geom_bar()+
    scale_fill_manual(values=c("#6e7cb9","#7bbcd5", "#f5db99"))+
  geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.25)+
  theme_bw()+
  theme(legend.position="none",panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())
```

### Final Typologies

```{r echo=FALSE, message=FALSE, warning=FALSE}
mapview(typology, zcol = "ctypo", col.regions = cp) + mapview(lease_areas, col.regions = "magenta") + mapview(planning_areas, col.regions = "lightpink")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(typology, aes(x=ctypo, fill = ctypo)) + 
  geom_bar()+
  geom_text(stat='count', aes(label=after_stat(count)), size = 2.5,vjust=-0.25)+
  labs(x = "Typology")+
  theme_bw()+
scale_fill_manual(values = cp)+
#  scale_fill_viridis(discrete = TRUE, option = "D") +
 #scale_fill_manual(values = c("#2f4f4f","#556b2f","#a0522d","#483d8b","#008000","#3cb371","#bc8f8f","#b8860b","#bdb76b","#000080","#20b2aa","#32cd32","#8b008b","#b03060","#ff4500","#ff8c00","#ffd700","#00ff00","#9400d3","#00fa9a","#dc143c","#00bfff","#0000ff","#adff2f","#b0c4de","#ff00ff","#6495ed","#dda0dd","#ff1493","#7b68ee","#ffa07a","#7fffd4","#ffdab9"))+
    theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),legend.title=element_blank(),panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

```

### Port Communities

Typologies of communities 5000 meters from a port listed as suitable in the [The Impacts of Developing a Port Network for Floating Offshore Wind Energy on the West Coast of the United States](https://www.nrel.gov/docs/fy23osti/86864.pdf) report
```{r echo=FALSE, message=FALSE, warning=FALSE}
mapview(port_typology, zcol = "ctypo", col.regions = cp2, legend = T) + mapview(ports, col.regions = "black",cex = 3, legend = F) + mapview(lease_areas, col.regions = "magenta") + mapview(planning_areas, col.regions = "lightpink")

```